---
title: "DeepSpot Beta"
output: 
  flexdashboard::flex_dashboard:
    theme: paper
    orientation: rows
    vertical_layout: fill
    social: menu
runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(tensorflow)
library(knitr)
library(DT)

options(DT.options = list(pageLength = 3, dom = 't'))
```


Sidebar {.sidebar data-width=350}
=====================================

DeepSpot is a user-friendly neural networks API. This application uses the **Inception-v3 model**, with pre-trained weights and
adjusted to predict leaf diseases in wheat images classes including:

- TanSpot
- Powdery Mildew
- Healthy Leaves
- Dry leaves



```{r}
# shiny inputs defined here
fileInput("file1", "Select an image from your local machine:", accept = c(".jpg", ".jpeg", ".png"))
selectInput("n_classes", label = "Number of Classes:",
            choices = seq_len(4), selected = 2)

```



Model {data-icon="fa-magic"}
=====================================  

Row {data-height=750}
-------------------------------------


### Image Preview

```{r}
renderImage({

  src <- input$file1
  src <- src$datapath

    if (is.null(src)) {
      list(src = "www/test0.jpg",
      height = "450",
      alt = "This is alternate text")
    } else {
      # Return a list
      list(src = src,
      height = "450",
      alt = "This is alternate text")
    }
      
  }, deleteFile = FALSE)
```
   

Row
-------------------------------------

### Results 

```{r, global, include=FALSE}
# instantiate the model
source('predict.R', local = TRUE)
```


```{r, results}
renderDT({
    # input$file1 will be NULL initially. After the user selects
    # and uploads a file, it will be a data frame with 'name',
    # 'size', 'type', and 'datapath' columns. The 'datapath'
    # column will contain the local filenames where the data can
    # be found.
    inFile <- input$file1

    if (is.null(inFile))
      return(NULL)

    withProgress(message = 'Predicting...', value = 1, {
      
    # load the image (copy an image from Photos)
    img_path <- inFile$datapath
    # img <- image_load(img_path, target_size = c(224,224))
    # x <- image_to_array(img)
    # 
    # # ensure we have a 4d tensor with single element in the batch dimension,
    # # the preprocess the input for prediction using resnet50
    # x <- array_reshape(x, c(1, dim(x)))
    # x <- imagenet_preprocess_input(x)
    # 
    # # make predictions then decode and print them
    # preds <- model %>% predict(x)
    # 
    # # table mods
    # main = imagenet_decode_predictions(preds, top = 3)[[1]]
    # main$explore_class_on_imagenet <- sprintf('Explore %s on ImageNet', main$class_name, main$class_description)
    
    main = predict_leafdisease(img_path, top = as.numeric(input$n_classes))
    
    DT::datatable(main)
    
    return(main)
  }) # end of progress message
}, escape = FALSE)
```
      
Team {data-icon="fa-people-carry"}
===================================== 

**Where**

We work at Embrapa Trigo a research unity from Brazilian Agricultural Research Corporation, located
at Passo Fundo/RS.

For more informations about us [follow](https://www.embrapa.br/trigo)

**Who**

- [Flavio Martins Santana](https://www.embrapa.br/equipe/-/empregado/322770/flavio-martins-santana) 
- [Eduardo Caierão](https://www.embrapa.br/equipe/-/empregado/316379/eduardo-caierao) 
- [Sandra Maria Mansur Scagliusi](https://www.embrapa.br/equipe/-/empregado/316783/sandra-maria-mansur-scagliusi) 
- [Marcia Barrocas Moreira Pimentel](https://www.embrapa.br/equipe/-/empregado/302758/marcia-barrocas-moreira-pimentel) 
- [Marcio Nicolau](https://www.embrapa.br/equipe/-/empregado/325170/marcio-nicolau) 
- [Claudia Cristina Clebsch](https://www.embrapa.br/equipe/-/empregado/325169/claudia-cristina-clebsch)
- [Diego Inacio Patricio](https://www.embrapa.br/equipe/-/empregado/355528/diego-inacio-patricio)

   
Resources {data-icon="fa-bookmark"}
===================================== 

**What the heck is a Deep Learning model?**

A Deep Learning model (neural net/work) is essentially a bunch of linear models stitched together, capable of abstracting complex non-linear relationships from the training data. These models allow for the modeler to focus on hyper parameter tuning instead of feature engineering.

**What is a pre-trained model?**

A pre-trained model is one which has been previously trained on a similar task other than the current one. It has two parts – model architecture and model weights. 

**What are the benefits and tradeoffs?**

A pre-trained model, while not 100% accurate still provides a very useful starting point because the features learned while training on the former task are useful for the new task. [4]  
Tranfering the learnings from the pre-trained model reduces the computational cost from developing a neural net from scratch. 

_____
  
Here are a list of tutorials and papers about Deep Learning & Image Classification:
  
1. [DataCamp's Keras Deep Learning R Tutorial](https://www.datacamp.com/community/tutorials/keras-r-deep-learning)
2. [Deep Residual Learning for Image Recognition](https://arxiv.org/abs/1512.03385)  
3. [Keras Tutorial: Using pre-trained Imagenet models](http://www.learnopencv.com/keras-tutorial-using-pre-trained-imagenet-models/)
4. [Keras Pretrained models from Kaggle](https://www.kaggle.com/gaborfodor/keras-pretrained-models)
5. [Transfer learning & The art of using Pre-trained Models in Deep Learning](https://www.analyticsvidhya.com/blog/2017/06/transfer-learning-the-art-of-fine-tuning-a-pre-trained-model/)
6. [useR 2016 Machine Learning Algorithmic Deep Dive Tutorial](https://github.com/ledell/useR-machine-learning-tutorial/blob/master/deep-neural-networks.ipynb)
7. [Transfer Learning](https://en.wikipedia.org/wiki/Transfer_learning)
8. [Tensorflow Package](https://tensorflow.rstudio.com/)
9. [Keras Package](https://keras.rstudio.com/)
